Assessing glymphatic transport velocities by adjoint methods

### 2018-10-01 tex/paper.tex
updaet

The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} which later was found to be particularly active during sleep~\cite{xie2013sleep}. 
It has been proposed that this pathway plays an important role in the waste
clearance of the brain. In particular, since the brain lack a lymphatic system, 
which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
The glymphatic system remains controversial and modeling attempts
has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
understanding of the pathway has significant potential because
dementia such as Alzheimer´s and Parkinson´s diseases are
associated with accumulation of metabolic waste such as
amyloid-beta and CSF-tau.

>>>>

A novel pathway called the paravascular pathway was discoved in 2011~\cite{iliff2012paravascular} and later found to be particularly active during sleep~\cite{xie2013sleep}. 
It has been proposed that this pathway plays an important role in the waste
clearance of the brain. In particular, since the brain lack a lymphatic system, 
which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
The glymphatic system remains controversial and modeling attempts
has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
understanding of the pathway has significant potential because
dementia such as Alzheimer´s and Parkinson´s diseases are
associated with accumulation of metabolic waste such as
amyloid-beta and CSF-tau.
